Interactive Checks for Coordination Avoidance

### 2019-08-16 doc/vldb_slides/sections/evaluation.tex
Finished first cut at speaker notes.

\begin{frame}[fragile]
  \begin{verbatim}
checker = InteractiveInvariantConfluenceChecker()
x = checker.int_max('x', 0) # An int, x, merged by max.
y = checker.int_max('y', 0) # An int, y, merged by max.
checker.add_transaction('inc_x', [x.assign(x + 1)])
checker.add_transaction('dec_y', [y.assign(y - 1)])
checker.add_invariant(x * y <= 0)
checker.check()\end{verbatim}
\end{frame}

@@

  \pause
  All run in less than a second and are implemented in less than 75 lines of
  specification.
\end{frame}

\begin{frame}
  \includegraphics[width=\textwidth]{assets/throughput_vs_fraction_16.pdf}
\end{frame}

\begin{frame}
  \begin{center}
    \Huge
    Come to our poster tomorrow night!
  \end{center}
\end{frame}

\begin{frame}
  \begin{center}
    \Huge
    Thank you
  \end{center}
\end{frame}

>>>>

\begin{frame}[fragile]
  \begin{verbatim}
checker = InteractiveInvariantConfluenceChecker()
x = checker.int_max('x', 0) # An int, x, merged by max.
y = checker.int_max('y', 0) # An int, y, merged by max.
checker.add_transaction('inc_x', [x.assign(x + 1)])
checker.add_transaction('dec_y', [y.assign(y - 1)])
checker.add_invariant(x * y <= 0)
checker.check()\end{verbatim}

  \note{%
    Finally, I'll give a teaser of our evaluation. We implemented our decision
    procedure in Python. You can specify objects, transactions, and invariants
    with code that looks like this.
  }
\end{frame}

@@

  \pause
  All run in less than a second and are implemented in less than 75 lines of
  specification.

  \note{%
    We specified a bunch of examples including things involving foreign keys,
    an auction application, something involving escrow transactions, and TPC-C.
    All the examples verify with a runtime of less then a second and every one
    is implemented in fewer than 75 lines of specification.
  }
\end{frame}

\begin{frame}
  \includegraphics[width=\textwidth]{assets/throughput_vs_fraction_16.pdf}

  \note{%
    We have some graphs showing that no coordination vastly outperforms
    replicating with strong consistency, and how segmented invariant confluence
    allows a smooth tradeoff between the two.
  }
\end{frame}

\begin{frame}
  \begin{center}
    \Huge
    Come to our poster tomorrow night!
  \end{center}

  \note{%
    I've jumped over a ton of details in the paper, and some things I didn't
    even mention at all. If you're curious about anything, I encourage you to
    come to our poster tomorrow night where I'm happy to chat.
  }
\end{frame}

\begin{frame}
  \begin{center}
    \Huge
    Thank you
  \end{center}

  \note{%
    Thank you all for listening, and I'm happy to take questions.
  }
\end{frame}

### 2019-08-16 doc/vldb_slides/sections/four_wise_men.tex
Added four wise men poem
Finished first cut at speaker notes.

    Imagine you're an application developer and you're trying to decide what
    kind of consistency you'd like to use to replicate some of your data.
  }
\end{frame}

@@

  \note{%
    Someone like Werner Vogels would probably tell you to use weak consistency.
    You can implement weak consistency super duper fast, and for many
    applications, weak consistency is good enough.
  }
\end{frame}

@@

  \note{%
    But then Tony Hoare laments, ``no no no''. Hoare encourages us not to
    settle for weak consistency because a weakly consistent system is hard to
    reason about. It robs us of a fundamental way we use to reason about
    programs: application invariants. Even if every transaction in a weakly
    consistent system preserves application invariants, the whole system may
    not.
  }
\end{frame}

@@

  \note{%
    Leslie Lamport chimes in agreeingly. He encourages us to choose strong
    consistency. Strongly consistent systems are much easier to reason about.
    After all a strongly consistent system to end users looks exactly like a
    system that's not even distributed.
  }
\end{frame}

@@

  \note{%
    ``Aha, not so fast'' counters Eric Brewer! Consistency and availability and
    partition tolerance, oh my. Surely, strong consistency comes at the price
    of availability and performance.

    So we're in a bit of a pickle. Weak consistency is too confusing and strong
    consistency is too heavy handed.
  }
\end{frame}

@@

  \note{%
    Thankfully, Peter Bailis comes to save the day and reminds us that perhaps
    we can have the best of both worlds. In 2014, Peter and some other smart
    folks including Alan defined invariant confluence as a condition under
    which we can replicate a piece of data without the need for strongly
    consistent coordination while maintaining the data's application
    invariants.

>>>>

    I'd like to begin my talk, if you don't mind, with a short fairy tale. The
    fairy tale involves an application developer who has some data they need to
    replicate. Unfortunately, the application developer cannot decide whether
    to replicate with weak consistency or strong consistency. The application
    developer stays up all night trying to decide but eventually falls asleep
    at their desk. In their sleep, they are visited by four wise men.

    % Imagine you're an application developer and you're trying to decide what
    % kind of consistency you'd like to use to replicate some of your data.

  }
\end{frame}

@@

  \note{%
    % Someone like Werner Vogels would probably tell you to use weak consistency.
    % You can implement weak consistency super duper fast, and for many
    % applications, weak consistency is good enough.

    ``Weak. Weak. It's weak that you're seeking'', squeaked Werner Vogels.
    His voice trembled, creaking, as he kept speaking.
    ``Please learn that if you yearn your performance to peak,
    then turn no further than weak.'' critiqued Werner.

    Werner Vogels has a good point. You can implement weak consistency super
    duper fast, and for many applications, weak consistency is good enough. But
    anyway, let's continue.
  }
\end{frame}

@@

  \note{%
    % But then Tony Hoare laments, ``no no no''. Hoare encourages us not to
    % settle for weak consistency because a weakly consistent system is hard to
    % reason about. It robs us of a fundamental way we use to reason about
    % programs: application invariants. Even if every transaction in a weakly
    % consistent system preserves application invariants, the whole system may
    % not.

    ``No, no, no more'' groaned Tony Hoare.
    He moaned, he lamented, his soul was tormented
    ``Weak is not easy. Weak is just treason.
    Please, these anomalies, make it so hard to reason.''

    You see, Hoare encourages us not to settle for weak consistency because a
    weakly consistent system is very hard to reason about.
  }
\end{frame}

@@

  \note{%
    % Leslie Lamport chimes in agreeingly. He encourages us to choose strong
    % consistency. Strongly consistent systems are much easier to reason about.
    % After all a strongly consistent system to end users looks exactly like a
    % system that's not even distributed.

    ``You see, I agree'', says he, the ever mesmerizing Leslie.
    ``Weak is just wrong, not right for long.
    To defend your end users, you must go with strong.''

    Leslie Lamport encourages us to choose strong consistency. Strongly
    consistent systems are much easier to reason about. After all a strongly
    consistent system to end users looks exactly like a system that's not even
    distributed.
  }
\end{frame}

@@

  \note{%
    % ``Aha, not so fast'' counters Eric Brewer! Consistency and availability and
    % partition tolerance, oh my. Surely, strong consistency comes at the price
    % of availability and performance.
    %
    % So we're in a bit of a pickle. Weak consistency is too confusing and strong
    % consistency is too heavy handed.

    ``Alas, not so fast'', Brewer the dapper chap clapped back.
    ``Consistency weak but not weary, strong but not nearly
    as fast as you think when you know my CAP theory.''

    Eric Brewer is right. Surely, strong consistency comes at the price of
    availability and performance. So our application developer is in a bit of a
    pickle. Weak consistency is too confusing and strong consistency is too
    heavy handed. Fortunately, a hero emerges to save the day.
  }
\end{frame}

@@

  \note{%
    But then out teetered Peter, with swagger demeanor.
    ``Why not have both?'' quoth Peter.
    The end.

    Peter Bailis comes to save the day and reminds us that perhaps we can have
    the best of both worlds. In 2014, Peter and some other smart folks
    including Alan defined invariant confluence as a condition under which we
    can replicate a piece of data without the need for strongly consistent
    coordination while maintaining the data's application invariants.
